Chapter 2 Draft

### 2020-04-14 Rmd/Draft.Rmd
taxsize citation
Organizing figures and ideas

@@

3) Can we predict the diversity of pollinator interactions with the phylogenetic distance of a community? Communities with a higher number o close related species will likely have trait redundancy and less diversity of interactions.

*Species/network metrics centrality/specialization

@@

This research has collated networks from 25 different studies from very different geographical regions across the world. Our aim is to have a good representation of the diversity of plant-pollinator interanctions that can take place with multiple combinations of plan traits and pollinator guilds. The networks of these studies that were done in consecutive years or in areas close to each other with a similar species compositon were combined in metawebs. This makes a total of 30 different unique networks/metawebs. For all of these studies we have done an extensive literature and online search of different floral traits. These traits are breeding system, compatibility system, selfing rate (with fruit and seed set), flower shape, flower symmetry, flower size (width and length), style length and ovule number. Moreover, we also recorded plant height, life span and life form for these species. These networks have weighted and unweighted data.

All plant and pollinator species names from these networks were searched through the Package taxsize from two different data sources ncbi and itis, respectively. Two of the main data sources for taxonomic names

#Methods

kable(m, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T)
```
\end{landscape}

@@

**PLOT 1**

Here I show the percentage or orders from the different species without consider visitation and just richness of species. Therfore, if we have a network with 4 species from from different orders, each will appear as 25% within the stack bar of the barplot.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8}
library(dplyr)
library(tidyr)
library(plyr)
library(ggplot2)
library(reshape2)
library(scales)
library(devtools)
library(png)
library(grid)
library(gridExtra)
library(jpeg)
dev_mode(on=T)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8}
library(dplyr)
library(tidyr)
library(plyr)
library(ggplot2)
library(reshape2)
library(scales)
library(devtools)
library(png)
library(grid)
library(gridExtra)
library(jpeg)
dev_mode(on=T)

@@

\newpage
**PLOT 2**

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center'}
library(ggplot2)
library(scatterpie)
library(sf)
world <- map_data('world')
setwd("~/R_Projects/Reproductive Traits")
data_merged_sub_ord <- readRDS("Data/RData/Breeding_systems_plot.RData")

@@

**PLOT 3**

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center'}
library(ggplot2)
library(scatterpie)
library(sf)
world <- map_data('world')
setwd("~/R_Projects/Reproductive Traits")
data_merged_sub_ord <- readRDS("Data/RData/Compatibility_system_plot.RData")

@@

**PLOT 4**

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center'}
library(ggplot2)
library(scatterpie)
library(sf)
world <- map_data('world')
setwd("~/R_Projects/Reproductive Traits")
data_merged_sub_ord <- readRDS("Data/RData/Life_Form_plot.RData")

@@

>>>>

**Research questions**

@@

3) Can we predict the diversity of pollinator interactions with the phylogenetic distance of a community? -Hypothesis- communities with a higher number o close related species will likely have trait redundancy and less diversity of interactions.

@@

This research has collated networks from 25 different studies from very different geographical regions across the world. All of these networks are from natural habitats or systems with a minor human intervention. The nature of these networks is both weighted (N) and unweighted (N) with the former just with visitation data which could serve as proxy of pollination with pollinator efficiency as limitation (REF). These studies have been counducted with different sampling methodologies and sampling effort and our aim is not to compare them but to get a general picture of how the selected functional traits shape these networks and the different taxonomic groups. The networks of these studies that were done in consecutive years or in areas close to each other with a similar species compositon were combined in metawebs. This makes a total of 30 different unique networks/metawebs when all are considered by their maximum level of organization (metaweb if possible). All the species names were searched with the help of the package taxsize [@chamberlain2013taxize] from two different data sources ncbi and itis, for plants and floral visitors respectively. We filled the not found searches manually with the help of <http://www.theplantlist.org/> and <http://www.mobot.org/> for plants and  <http://www.catalogueoflife.org/> for floral visitors.

For all of these studies we have done an extensive literature and online search of different floral traits. These traits are breeding system, compatibility system, selfing rate (with fruit and seed set), flower shape, flower symmetry, flower size (width and length), style length and ovule number. Moreover, we also recorded plant height, life span and life form for these species.

@@

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8, fig.cap="Percentage of species of each order per network/metaweb (qualitative data)."}
library(dplyr)
library(tidyr)
library(plyr)
library(ggplot2)
library(reshape2)
library(scales)
library(devtools)
library(png)
library(grid)
library(gridExtra)
library(jpeg)
dev_mode(on=T)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8, fig.cap="Percentage of visits of each order per network/metaweb (quantitative data)."}
library(dplyr)
library(tidyr)
library(plyr)
library(ggplot2)
library(reshape2)
library(scales)
library(devtools)
library(png)
library(grid)
library(gridExtra)
library(jpeg)
dev_mode(on=T)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.cap="Pie charts on the coordinates of each study site  with a classification of three main breeding systems (hermaphroditism, dioecy and monoecy)."}
library(ggplot2)
library(scatterpie)
library(sf)
world <- map_data('world')
setwd("~/R_Projects/Reproductive Traits")
data_merged_sub_ord <- readRDS("Data/RData/Breeding_systems_plot.RData")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.cap="Pie charts on the coordinates of each study site  with the compatibility level classified in three main groups (self compatible, partially self compatible and self incompatible)."}
library(ggplot2)
library(scatterpie)
library(sf)
world <- map_data('world')
setwd("~/R_Projects/Reproductive Traits")
data_merged_sub_ord <- readRDS("Data/RData/Compatibility_system_plot.RData")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.cap="Pie charts on the coordinates of each study site  with the life forms for all the species divided in trees, shrubs, herbs and vines."}
library(ggplot2)
library(scatterpie)
library(sf)
world <- map_data('world')
setwd("~/R_Projects/Reproductive Traits")
data_merged_sub_ord <- readRDS("Data/RData/Life_Form_plot.RData")

@@

kable(m, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", caption = "Metadata for all the different networks/metawebs used at their maximum level of organization (metaweb if possible).") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T)
```
\end{landscape}
